Background Subtraction via Deep Variation Transformation

### 2018-08-15 draft.tex
公式

%具体介绍
% XXX 一句话，换一行！！！
% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
In the DVTL model, 
the sequence of pixel observations is used to represent the variation and input into the network for learning,
which encode both the intensity distribution and sequential information.
%
Then, a Fully Convolutinal Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
%
In particular,
we take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
%
Benefited from the strong learning ability of FCN,
proposed approach works well in diversely complex scenes adaptively.
%
%Moreover,
%since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
% 
% 
% 
% \todo{This paragraph is too short! provide comprehensive details of our work!}
% % The final prediction can be obtained by thresholding of the transformed variation. 
% %Our contributions can be summarized as follows:
% The contridbutions of proposed approach are shown as follows:
% \begin{itemize}
% \item We proposed the pixel observation matrix to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
%     The observation matrix is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
% \item We propose a deep neural network for variation transformation. 
%     Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
% \end{itemize}
% 
%文章结构

@@

%GMM
The most famous pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time. Pixels are considered to be background if there exists a Gaussian includes their values with sufficient evidence. 
%GMM+
Zoran Zivkovic\cite{Zivkovic2004} extend the GMM through the use of recursive equations, where the parameters keep constantly updating and the number of components are adaptable to each pixel. 
%你的ICME那篇里面也用过extend through the use of 这句话的啊。 这里的改进就是用了一些回归方程，我也从别的文章里看过的。
%codebook
Some other popular algorithms in pixel based category are based on Codebook. 
In \cite{Kim2005}, Kim et al present the codebook method to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model. The final foreground is detected by a distance measurement in a cylindrical color model.
%KDE
A non-parametric background model is proposed in \cite{Elgammal2000Non}. Elgammal et al. assume that each background pixel is drawn from a Probability Distribution Function(PDF). The PDF for each pixel is estimated with Kernel Density Estimation(KDE). 
%Vibe
Another non-parametric method is proposed by O. Barnich, called the Visual Background Extractor (ViBe)\cite{Barnich2011_2011_TIP}. ViBe is a sample based method, which consists of pixel samples from the video stream. Each pixel in the current frame is compared with N pixel samples from the corresponding background model. A pixel is labeled as the foreground only when there exist at least K samples with a distance to itself within a certain range R. 
%PBAS
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.

@@

\section{VARIATION TRANSFORMATION}
\label{sec3}
In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation works in background subtraction.

@@

%第四步空间近邻随机采样。
It is generally accepted that, neighboring background pixels share a similar temporal variation. 
In order to benefit from the spatial context, we cascade the pixel matrix with 3 neighboring pixel matrixes randomly selected in 8 nearest neighbors, as shown in \reffig{flow_chart}. 
Now, we have the input of our network, which size is $d\times d\times 4$.

In the previous steps, videos are broken down into pixel matrixes which containing abundant background information. 
Next, the groundtruth matrixes are obtained in the same way, except the cascading process. 
Both of them are put into the network for the training. 
However, the size of the input will decreased in the forward computation. 
In order to make output the same size as input, we borrowed ideas from Image Semantic Segmentation \cite{Shelhamer2017fcn}, which is doing padding to the input before the training. 
After the forward computing, variations are transformed in a new space where they can be easily classified by thresholding. 
The new representation of input pixel variation is defined as:
\begin{equation}
H_p= \mathcal L (E_x (H)),
\end{equation}

Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$. 
Another advantage of symmetric padding is that the order information still remains.

>>>>

%具体介绍
% XXX 一句话，换一行！！！
% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
In the DVTL model, 
the sequence of pixel observations is used to represent the variation and input into the network for learning,
which encode both the intensity distribution and sequential information.
%
Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantee the linear separability of transformed pixel variation generated by mapping in a new space.
%
In particular,
we take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
%
Benefited from the strong learning ability of FCN,
proposed approach works well in diversely complex scenes adaptively.
%
%Moreover,
%since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
% 
% 
% 
% \todo{This paragraph is too short! provide comprehensive details of our work!}
% % The final prediction can be obtained by thresholding of the transformed variation. 
% %Our contributions can be summarized as follows:
% The contridbutions of proposed approach are shown as follows:
% \begin{itemize}
% \item We proposed the pixel observation matrix to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
%     The observation matrix is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
% \item We propose a deep neural network for variation transformation. 
%     Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
% \end{itemize}
% 
%文章结构

@@

%GMM
The most famous pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, which utilize a mixture of weighted Gaussians to model the probability distribution of each pixel over time. Pixels are considered to be background if there exists a Gaussian includes their values with sufficient evidence. 
%GMM+
Zoran Zivkovic\cite{Zivkovic2004} extend the GMM through the use of recursive equations, where the parameters keep constantly updating and the number of components are adaptable to each pixel. 
%你的ICME那篇里面也用过extend through the use of 这句话的啊。 这里的改进就是用了一些回归方程，我也从别的文章里看过的。
%codebook
Some other popular algorithms in pixel based category are based on Codebook. 
In \cite{Kim2005}, Kim et al present the codebook method to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model. The final foreground is detected by a distance measurement in a cylindrical color model.
%KDE
A non-parametric background model is proposed in \cite{Elgammal2000Non}. Elgammal et al. assume that each background pixel is drawn from a Probability Distribution Function(PDF). The PDF for each pixel is estimated with Kernel Density Estimation(KDE). 
%Vibe
Another non-parametric method is proposed by O. Barnich, called the Visual Background Extractor (ViBe)\cite{Barnich2011_2011_TIP}. ViBe is a sample based method, which consists of pixel samples from the video stream. Each pixel in the current frame is compared with N pixel samples from the corresponding background model and labeled as the foreground when there exist at least K samples with a distance to itself within a certain range R. 
%PBAS
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.

@@

\section{VARIATION TRANSFORMATION}
\label{sec3}
In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation work in background subtraction.

@@

%第四步空间近邻随机采样。
It is generally accepted that neighboring background pixels share a similar temporal variation.
In other words, there are some clues hidden in pixels' spatial neighbors. 
In order to benefit from the spatial context, we concatenate the pixel matrix with 3 neighboring pixel matrixes, denoted as $SM_1$, $SM_2$ and $SM_3$ respectively.
They are randomly selected in 8 nearest neighbors. 
The input matrix of our network is defined as:
\begin{equation}
H = C(H^m, SM_1, SM_2, SM_3),
\end{equation}

Where $C$ represents the concatenating process on the third dimension.
And $H$ is the input matrix of our network, which size is $d\times d\times 4$.

In the previous steps, videos are broken down into pixel matrixes which contain abundant background information. 
Next, the groundtruth matrixes are obtained in the same way, except the concatenating process. 
Both of them are put into the network for the training. 
However, the size of the input will decreased in the forward computation. 
In order to make output the same size as input, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input matribxes before the training. 
After the forward computing, variations are transformed in a new space where they can be easily classified by thresholding. 
The transformed pixel variation is defined as:
\begin{equation}
H_p= \mathcal L (E_x (H)),
\end{equation}

Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $\mathcal L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$. 
Another advantage of symmetric padding is that the order information still remains.
